Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex

Our proof of Lemma~\ref{lem:soundness} actually turned out to be instructive
because it forced us to recognize that the original formulation in Simonet and
Pottier's paper on \origLang~\cite{InfoFlowML} wasn't quite correct.
Specifically, it is entirely possible that a step in the operational semantics
does not translate to a step in the operational semantics under either
projection, as in the case of the \ref{eq:lift-app} rule, where $\lift{e}_i$ and
$\lift{e'}_i$ are identical.  Luckily, we are fairly confident, given that we
were still able to prove Lemma~\ref{lem:stuck_bracket} despite this change, that
this is not a critical error in the original paper.

\todo{More.}

>>>>

\subsection{Inaccuracies in the Original Proof}

We discovered a few small inaccuracies in \cite{InfoFlowML} by running into
issues when formalizing the proofs in Coq.  Listed below are the primary
corrections we were able to make.

\begin{description}
  \item[Non-nesting Brackets in Syntax]
    \hspace{0pt}

    As seen in Figure~\ref{fig:syntax}, we have a slightly different syntax
    structure for \langName from \origLang.  Specifically, we constructed
    values, answers, and expressions explicitly to not allow nesting of
    bracketed values.  This was not how the syntax figures in Simonet and
    Pottier's paper defined this, and as a result, we had trouble when our
    proofs depended on this explicit non-nesting property that was mentioned in
    the prose of their paper.  Realizing that our definitions did not disallow
    this by construction after running into issues in the proof, we were able to
    fix the definition producing what is in Figure~\ref{fig:syntax}.

  \item[Correction of the Soundness Lemma]
    \hspace{0pt}

    Proving our own version of Lemma~\ref{lem:soundness} actually turned out to
    be instructive because it forced us to recognize that the original
    formulation in Simonet and Pottier's paper on \origLang wasn't exactly
    correct as stated.  Specifically, it is entirely possible that a step in the
    operational semantics does not translate to a step in the operational
    semantics under either projection, as in the case of the \ref{eq:lift-app}
    rule, where $\lift{e}_i$ and $\lift{e'}_i$ are identical.  Luckily, we are
    fairly confident, given that we were still able to prove
    Lemma~\ref{lem:stuck_bracket} despite this change, that this is not a
    critical error in the original paper.
\end{description}

\todo{more?}
